---
title: "TREAT Accrual Report"
output:
  word_document: 
    reference_docx: word_styles.docx
  html_document: default
date: " "
---
---

* TREAT-001 -- Observational 
* TREAT-002 -- IU Obeticholic Acid 
* TREAT-003 -- VCU Immuron 
* TREAT-008 -- Cohort Dose Escalation Study  


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pander)
library(grid)
library(gridExtra)
```

```{r, echo=FALSE}
#Code as function with arguments (on study dates, start date, end date of the accrual, 
#   expected end date of accrual, expected n per month )
accrualGraph = function(ondate, startdate, enddate=Sys.Date(), expenddate=Sys.Date(), expmnth=0) {
  #install pacakges (if not installed) and load
  packages <- c("ggplot2", "scales")
  if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
    install.packages(setdiff(packages, rownames(installed.packages())))  
  }  
  library(ggplot2)
  library(scales)
  
  #Build monthly buckets of actual accrual
  mnths = seq(startdate, enddate, by="month")
  
  # create variables of the week and month of each observation:
  enroll <- data.frame(ondate)
  enroll$Month <- as.Date(cut(as.Date(enroll$ondate,format="%m/%d/%Y"),breaks = "month"))
  enroll$Count = 1
  
  #possible that a month would not have any enrollment, need to add months with no enrollment
  dmnth = as.Date(unique(enroll$Month))
  addmnth = mnths[!mnths %in% dmnth]
  enroll2 = enroll
  enroll2[(nrow(enroll)+1):(nrow(enroll)+length(addmnth)),"Month"] = addmnth
  enroll2[(nrow(enroll)+1):(nrow(enroll)+length(addmnth)),"Count"] = 0
  
  # sum by month and assign total for each month into Accrual vector, since month buckets
  # are summed into beginning of first month, need to move sums one month over for end-of-month
  msum = c(0,cumsum(as.vector(unlist(tapply(enroll2$Count,enroll2$Month,sum)))))
  
  
  #since seq of months was built by month the enddate will always be the first of the month 
  if(!enddate %in% mnths) {
    mnths = append(mnths, enddate)
  }
  
  acc = data.frame(mnths,msum)
  acc$accgrp="Actual"
  
  #append expected month sequence into graph data if it was passed to function
  if(!expmnth==0){
    expmnths =   seq(startdate, expenddate, by="month")
    expdf = data.frame(mnths=expmnths,msum=seq(from=0,to=(expmnth*(length(expmnths)-1)),by=expmnth),accgrp="Expected")
    acc = rbind(acc, expdf)
  }
  
  # graph by month:
  ggplot(data = acc, aes(mnths, msum,group=accgrp,colour=accgrp)) +
    geom_line(aes(linetype=accgrp)) +
    geom_point()  +
    xlab("Accrual Date") + ylab("Number of Patients Accrued") +
    scale_colour_discrete(name="") +    
    scale_linetype_discrete(name="")    
}
```
  
## TREAT 001 -- Observational


  
```{r, echo=FALSE}
#read xls or xlsx
library("readxl")

demog <- read_excel("I:/Projects/TREAT/Data Management/Reports/Enrollment Reports/data/Demographics_001.xlsx")
# demog <- read.delim("I:/Projects/TREAT/Data Management/Reports/Enrollment Reports/data/Demographics_001.txt")
demog2 = demog[which(demog$ARMS == "CASES" & demog$ELIGIBILITY_STATUS %in% c("Eligible", "Eligible(O)")),]
demog3 = demog[which(demog$ARMS == "CONTROLS" & demog$ELIGIBILITY_STATUS %in% c("Eligible", "Eligible(O)")),]

Site=c("IU","Mayo","VCU", "Total by Arm")
IU = c("Fairbanks Drug and Alcohol Rehabilitation Hospital", "Indiana University Hospital / IU Simon Cancer Center", "Eskenazi Hospital")
Mayo = "Mayo Clinic"
VCU = "Virginia Commonwealth University (VCU)"
# enrollment numbers by site and total for CASES
Cases=c(length(which(demog2$STUDY_SITE %in% IU)),length(which(demog2$STUDY_SITE %in% Mayo)), length(which(demog2$STUDY_SITE %in% VCU)),
          nrow(demog2))
Controls=c(length(which(demog3$STUDY_SITE %in% IU)),length(which(demog3$STUDY_SITE %in% Mayo)), length(which(demog3$STUDY_SITE %in% VCU)),
          nrow(demog3))
Total=c(Cases[1]+Controls[1], Cases[2]+Controls[2], Cases[3]+Controls[3], Cases[4]+Controls[4])
# pander(data.frame(Site,Cases, Controls, Total))
d = grid.table(data.frame(Site,Cases, Controls, Total), rows = NULL)
grid.draw(d)
```


### TREAT 001 -- Accrual by Month (All Sites - Cases)
```{r, echo=FALSE}
ondate = as.Date(na.omit(demog2$ON_STUDY_DATE), origin="1899-12-30")
#ondate = as.Date(demog$ON_STUDY_DATE, format="%m/%d/%Y")

#Code as function with arguments (on study dates, start date, actual end date, 
#  expected end date, optional expected n per month )
accrualGraph(ondate,startdate=as.Date("2013-06-01"),expmnth=7)

```

### TREAT 001 -- Accrual by Month (All Sites - Controls)
```{r, echo=FALSE}
ondate = as.Date(na.omit(demog3$ON_STUDY_DATE), origin="1899-12-30")
#ondate = as.Date(demog$ON_STUDY_DATE, format="%m/%d/%Y")

#Code as function with arguments (on study dates, start date, end date, 
#  optional expected n per month )
accrualGraph(ondate,startdate=as.Date("2013-06-01"),expmnth=4.5)

```

## TREAT 002 -- IU Obeticholic Acid

```{r, echo=FALSE}
#read xls or xlsx
library("readxl")

demog <- read_excel("I:/Projects/TREAT/Data Management/Reports/Enrollment Reports/data/Demographics_002.xlsx")
demog2 = demog[demog$ELIGIBILITY_STATUS %in% c("Eligible", "Eligible(O)"),]
Site=c("IU","Einstein", "Mayo","VCU", "Total")
IU = c("Fairbanks Drug and Alcohol Rehabilitation Hospital", "Indiana University Hospital / IU Simon Cancer Center", "Eskenazi Hospital")
Einstein = "Albert Einstein Health Network (site)"
Mayo = "Mayo Clinic"
VCU = "Virginia Commonwealth University (VCU)"
# enrollment numbers by site and total for CASES
Accrued=c(length(which(demog2$STUDY_SITE %in% IU)), length(which(demog2$STUDY_SITE %in% Einstein)),
          length(which(demog2$STUDY_SITE %in% Mayo)), length(which(demog2$STUDY_SITE %in% VCU)), nrow(demog2))  
# pander(data.frame(Site,Accrued))
d = grid.table(data.frame(Site,Accrued), rows = NULL)
grid.draw(d)

```

### TREAT 002 -- Accrual by Month (All Sites)

```{r, echo=FALSE}

ondate = as.Date(na.omit(demog2$ON_STUDY_DATE), origin="1899-12-30")

accrualGraph(ondate,startdate=as.Date("2014-12-01"),expenddate=as.Date("2016-03-01"),expmnth=4)

```

## TREAT 003 -- VCU Immuron

```{r, echo=FALSE}
#read xls or xlsx
library("readxl")

demog <- read_excel("I:/Projects/TREAT/Data Management/Reports/Enrollment Reports/data/Demographics_003.xlsx")
demog2 = demog[demog$ELIGIBILITY_STATUS %in% c("Eligible", "Eligible(O)"),]

Site=c("IU","Mayo","VCU", "Total")
IU = c("Fairbanks Drug and Alcohol Rehabilitation Hospital", "Indiana University Hospital / IU Simon Cancer Center", "Eskenazi Hospital")
Mayo = "Mayo Clinic"
VCU = "Virginia Commonwealth University (VCU)"
# enrollment numbers by site and total for CASES
Accrued=c(length(which(demog2$STUDY_SITE %in% IU)),length(which(demog2$STUDY_SITE %in% Mayo)), length(which(demog2$STUDY_SITE %in% VCU)),
                  nrow(demog2))
# pander(data.frame(Site,Accrued))
d = grid.table(data.frame(Site,Accrued), rows = NULL)
grid.draw(d)

```

### TREAT 003 -- Accrual by Month (All Sites)


```{r, echo=FALSE}

ondate = as.Date(na.omit(demog2$ON_STUDY_DATE), origin="1899-12-30")

accrualGraph(ondate,startdate=as.Date("2014-12-01"),expenddate=as.Date("2016-03-01"),expmnth=4.5)

```

## TREAT 008 -- Cohort Dose Escalation Study

```{r, echo=FALSE}
#read xls or xlsx
library("readxl")

demog <- read_excel("I:/Projects/TREAT/Data Management/Reports/Enrollment Reports/data/Demographics_008.xlsx")
demog2 = demog[demog$ELIGIBILITY_STATUS %in% c("Eligible", "Eligible(O)"),]


Site=c("IU","Mayo","VCU", "Total")
IU = c("Fairbanks Drug and Alcohol Rehabilitation Hospital", "Indiana University Hospital / IU Simon Cancer Center", "Eskenazi Hospital")
Mayo = "Mayo Clinic"
VCU = "Virginia Commonwealth University (VCU)"
# enrollment numbers by site and total for CASES
Accrued=c(length(which(demog2$STUDY_SITE %in% IU)),length(which(demog2$STUDY_SITE %in% Mayo)), length(which(demog2$STUDY_SITE %in% VCU)),
                  nrow(demog2))
# pander(data.frame(Site,Accrued))
d = grid.table(data.frame(Site,Accrued), rows = NULL)
grid.draw(d)

```

### TREAT 008 -- Accrual by Month (All Sites)


```{r, echo=FALSE}

ondate = as.Date(na.omit(demog$ON_STUDY_DATE), origin="1899-12-30")

accrualGraph(ondate,startdate=as.Date("2016-05-01"))

```
